A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-30 1_intro.tex
dash in contour-parallel
lil edit

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
Contour parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

@@

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where it has been shown that a wide range of widths could be realized by the hardware. 
For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
However, for FDM printing, it is challenging to realize varying width by extruding through a nozzle with a fixed size (the preferred width), either by varying the movement speed or by dynamically adjusting the volumetric flow rate. 
Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.

>>>>

FDM printers extrude semi-continuous beads of molten plastic through a nozzle, which moves along a planned toolpath within each layer of a 3D object.
A common strategy to accurately manufacture a given 3D model is to extrude along a contour-following path,
because the position and shape of the toolpath can be controlled relatively accurately.
Filling up a shape using parallel straight lines would expose defects of the size of the nozzle, which is generally an order of magnitude larger than the resolution of the positioning system.
Contour-parallel extrusion therefore leads to a less bumpy outline shape than direction parallel extrusion does.

@@

One promising direction to avoid over- and underfills is to employ toolpath with adaptive width. 
This strategy has been mostly investigated for metal additive manufacturing using wire and arc~\cite{Ding2014,Xiong2019}, where it has been shown that a wide range of widths could be realized by the hardware. 
For instance, \citeauthor{Ding2016a} developed a toolpath with an (estimated) width variation by a factor of up to $3$~\cite{Ding2016a}.
However, for FDM printing, it is challenging to accurately realize varying width by extruding material through a nozzle with a fixed size, either by varying the movement speed or by dynamically adjusting the volumetric flow rate. 
Therefore, a much narrower range of widths is desirable for robust FDM fabrication.
On the other hand, controlling the variation in width is beneficial for limiting the variation in mechanical properties of the resulting material fragments. 
% The bead width has been associated with total print time, the roughness of top surfaces, printing resolution and the strength of a part, through the contact area it makes with neighboring beads~\cite{N.Turner2014,ahn2002anisotropic}.
